\documentclass[12pt]{article}
\usepackage{sectsty}
\usepackage{titlesec}
%	options include 12pt or 11pt or 10pt
%	classes include article, report, book, letter, thesis

\title{Gaussian Process Regression}
\author{Prof. S.R Khare \\ Poorvi Agrawal}
\date{28 July 2015}

\begin{document}
\maketitle
\titleformat{\section}
{\normalfont\large\bfseries}{\thesection}{1em}{}
\section*{Regression}
Regression analysis is a technique for finding out the relationship between variables. It has a lot of real life
application. Be it for forecasting or to predict petrol prices for the next month, regression analysis is used
widely and in almost every field. It has been classified based on the dependence of variables: Linear
regression, nonlinear, logistic etc. Linear regression is commonly used approach for finding out the
relationship between one dependent variable and one or more independent variable.

\section*{Gaussian Process Regression}
Gaussian Process is a family of distribution where it may or may not depend on time. In Gaussian process,
every finite number of random variables follows multivariate normal distribution which is normal
distribution in higher dimension. Joint distribution of infinitely many random variables following above
criteria is the distribution of Gaussian process. It is mainly defined by two functions: mean and covariance
function. In Gaussian Process Regression, rather than specifying a function to a specific model like in linear
or quadratic regression, it defines function indirectly so that it would become less parametric which implies
fewer assumptions in data set, hence getting more accurate predictions. It has a wide application when it
comes to noisy data i.e. unwanted, inaccurate data.

\section*{Difference in Regression and Gaussian Process Regression}
Regression is considered to be an effective approach for modelling because of its simplicity in
implementation and analysis. But when it comes to flexibility, it is of no more advantageous. Regression
model can give poor predictions if function is not properly chosen. Gaussian process Regression is better
approach than normal regression as fixed there is no need for selecting a function which makes it more
accurate and flexible.

\end{document}